SubGenome Analysis

### 2017-07-27 R/SubGenome Analysis.Rmd
Minor changes

  #v1 vs. v1
  synMapOutputFile: "6807_8082.CDS-CDS.lastz.tdd10.cs0.filtered.dag.all.go_D20_g10_A5.aligncoords.gcoords.ks"
  inputDataFile: "../Data/sorghum_v1_vs_maize_v1.tab"
  outputFile: "../Output/recoveredSubGenomes_sorghum_v1_vs_maize_v1.tab"
  log10_ks_cutoff: -0.575

@@

# Reconstructed ancestral chromosomes
homeologs %>% group_by(org_chr1, org_chr2) %>% summarize(genes=sum(count)) %>% spread(org_chr2, genes) -> homeologs.spread
homeologs.spread$total <- rowSums(homeologs.spread[-1], na.rm = TRUE)
syntelogs.complete %>% select(org_chr1) %>% distinct() %>% left_join(homeologs.spread) %>% replace(is.na(.), 0) %>% arrange(desc(total)) -> homeologs.totals
```
```{r reportFindSubgenomes, echo=FALSE, results="asis"}
homeologs.totals %>% knitr::kable(caption = "Table")
homeologs.totals %>% filter(total==0) %>% nrow() %>% replace(is.na(.), 0) %>% sprintf("There are %i unaligned sorghum chromosome(s)", .) %>% cat()

>>>>

  #v1 vs. v1
  synMapOutputFile: "6807_8082.CDS-CDS.lastz.tdd10.cs0.filtered.dag.all.go_D20_g10_A5.aligncoords.gcoords.ks"
  inputDataFile: "../Data/sorghum_v1_vs_maize_v1.tab"
  outputFile: "../Output/recoveredSubGenomes_sorghum_v1_vs_maize_v1.tab"
  log10_ks_cutoff: 0
  #-0.575

@@

# Reconstructed ancestral chromosomes
homeologs %>% group_by(org_chr1, org_chr2) %>% summarize(genes=sum(count)) %>% spread(org_chr2, genes) -> homeologs.spread
homeologs.spread$total <- rowSums(homeologs.spread[-1], na.rm = TRUE)
syntelogs.complete %>% select(org_chr1) %>% distinct() %>% left_join(homeologs.spread) %>% replace(is.na(.), 0) %>% arrange(desc(org_chr1)) -> homeologs.totals
```
```{r reportFindSubgenomes, echo=FALSE, results="asis"}
homeologs.totals %>% knitr::kable(caption = "Table")
homeologs.totals %>% filter(total==0) %>% nrow() %>% replace(is.na(.), 0) %>% sprintf("There are %i unaligned sorghum chromosome(s) in the above table.", .) %>% cat()
